\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-08-21 paper.tex
Work on the 'Experimental Deployments'

Before introducing and explaining step-by-step a complete working example in the next
section, it is useful to first introduce the main concepts of \pyRobots, and
provide an overview of the features and mechanisms.

@@

\subsection{Platforms}

@@

\subsection{Experiments and studies}

@@

>>>>

Before introducing and explaining step-by-step a complete working example in the
next section, it is useful to first introduce the main concepts of \pyRobots,
and provide an overview of the features and mechanisms. Since \pyRobots is an
open-source software, the interested reader can also refer to the source code,
available here:~\url{https://github.com/chili-epfl/pyrobots}.

@@

The development of \pyRobots started in 2011, driven by the requirements of a
18-min long theatre performance between a human actor and a robot. Since that time, the toolkit has
iteratively matured, and has been deployed and used on several projects and
platforms. We first briefly recap these deployments with references to the
corresponding publications, and then present our latest study, in a nursery,
that recently acted as a stress-test for the library.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
\begin{center}
\begin{tabular}{p{0.9\columnwidth}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Examples of \pyRobots actions, mostly stemming from experiments involving
    the PR2 robot.}

\label{pyrobots_actions}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Roboscopie} The first complex deployment scenario for \pyRobots was indeed a theatre
performance entitled \emph{Roboscopie}~\cite{lemaignan2012roboscopie}. The
toolkit was created out of the need to control a complex robot (a Willow Garage
PR2) in a structured way, as required for a live performance with a
human\footnote{The original \pyRobots script used for the performance can be
accessed from~\url{http://www.laas.fr/roboscopie}. Note that this script does
not reflect anymore the toolkit usage.}

A total of 47 \pyRobots actions were written for this event
(Table~\ref{pyrobots_actions} gives a few examples), and the toolkit proved to
be especially convenient to interleave calls to both ROS-based and {\sc
GenoM}-based\footnote{{\sc GenoM} is software component as well as a middleware
developed at LAAS-CNRS} components through their respective Python bindings.

\pyRobots also allowed us to retain the \emph{rapid prototyping} convenience of a
script language, essential for the robot to ``practise'' and adapt to the
vision of the director.

@@

@@

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{cowriter}
        \caption{Children teaching An Aldebaran Nao interacting with }
        \label{expe-cowriter}
\end{figure}
